Using Monte Carlo to estimate the effects of NHL rule changes

### 2020-12-10 slides.Rmd
Add files via upload
added 2017-2018 graphics and results

---
title: "Using Monte Carlo to estimate the effects of NHL rule changes"
author: "Kilbourne, Michael, Clinton, Sam"
output: slidy_presentation 
---

@@

>>>>

---
title: "Using Monte Carlo to estimate the effects of NHL rule changes"
author: "Kilbourne Charrier, Michael Bauers, Clinton, Sam Downs"
output: slidy_presentation 
---

@@

# Results of 2017-2018

- Conference gap under the old alignment was estimated to be 0.038 
- Conference gap under the new alignment with 31 teams was estimated to be 1.091

# 2017-2018 Plots

![](Images/gapvis20172018.png)

# 2017-2018 Plots

![](Images/seedplace20172018.png)
